Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-02-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

%%%%%%%%%%%%%
\section{Conclusions}\label{Section:Conclusion}
\red{(1)Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by our work in the present manuscript;}
The purpose of this paper is to describe the fluid instabilities, in particular the viscous fingering, and demonstrate a new computational approach used in order to capture the finger development. Starting from validating the development of fingers in a computational domain against experimental setup a series of other computational cases is showed focusing on the details of the flows and the introduction of parameteres by avoiding any upscaling requirements.

>>>>

%%%%%%%%%%%%%
\section{Conclusions}\label{Section:Conclusion}
% Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by our work in the present manuscript;}
The purpose of this paper is to numerically investigate the dynamics of viscous flow instabilities in porous media. Simulations involving formation and growth of viscous fingers were conducted with the CVFEM-based multi-fluid flow simulator Fluidity/IC-FERST model. The model is based upon a dual consistent pressure-velocity representation in CV and FEM spaces and the novel family of FE-pairs, \PN[n]{m} and \PNDG[n]{m}. Saturation and other scalar fields (e.g., density, temperature etc) are discretised in CV space and may be fully discontinuous across finite element boundaries. Material absolute permeability is piecewise constant in FE space to ensure the correct representation of the surface .In order to strongly enforce the discretised Darcy equation in the boundaries between elements and control volumes, a directional-weighted flux-limited was introduced to take into account discontinuities risen from both, the numerical formulation (based on discontinuous-Galerkin finite element method, DGFEM) and control volumes within finite elements.

Starting from validating the development of fingers in a computational domain against experimental setup a series of other computational cases is showed focusing on the details of the flows and the introduction of parameteres by avoiding any upscaling requirements.
